% CPP

\section{Anexa 1. main.cpp}
\label{appendix:1_main_cpp}
\inputminted[linenos,tabsize=4,breaklines]{C++}{code/cpp/main.cpp}

\section{Anexa 2. Volume.h}
\label{appendix:2_volume_h}
\inputminted[linenos,tabsize=4,breaklines]{C++}{code/cpp/Volume.h}

\section{Anexa 3. Volume.cpp}
\label{appendix:3_volume_cpp}
\inputminted[linenos,tabsize=4,breaklines]{C++}{code/cpp/Volume.cpp}

\section{Anexa 4. Shader.h}
\label{appendix:4_shader_h}
\inputminted[linenos,tabsize=4,breaklines]{C++}{code/cpp/Shader.h}

\section{Anexa 5. Shader.cpp}
\label{appendix:5_shader_cpp}
\inputminted[linenos,tabsize=4,breaklines]{C++}{code/cpp/Shader.cpp}

\section{Anexa 6. Interface.h}
\label{appendix:6_interface_h}
\inputminted[linenos,tabsize=4,breaklines]{C++}{code/cpp/Interface.h}

\section{Anexa 7. Interface.cpp}
\label{appendix:7_interface_cpp}
\inputminted[linenos,tabsize=4,breaklines]{C++}{code/cpp/Interface.cpp}

\section{Anexa 8. VectorColorPicker.h}
\label{appendix:8_tfwidget_h}
\inputminted[linenos,tabsize=4,breaklines]{C++}{code/cpp/VectorColorPicker.h}

\section{Anexa 9. VectorColorPicker.cpp}
\label{appendix:9_tfwidget_cpp}
\inputminted[linenos,tabsize=4,breaklines]{C++}{code/cpp/VectorColorPicker.cpp}

\section{Anexa 10. SettingsEditor.h}
\label{appendix:10_settingsedit_h}
\inputminted[linenos,tabsize=4,breaklines]{C++}{code/cpp/SettingsEditor.h}

\section{Anexa 11. SettingsEditor.cpp}
\label{appendix:11_settingsedit_cpp}
\inputminted[linenos,tabsize=4,breaklines]{C++}{code/cpp/SettingsEditor.cpp}

\section{Anexa 12. Loader.h}
\label{appendix:12_loader_h}
\inputminted[linenos,tabsize=4,breaklines]{C++}{code/cpp/Loader.h}

\section{Anexa 13. Loader.cpp}
\label{appendix:13_loader_cpp}
\inputminted[linenos,tabsize=4,breaklines]{C++}{code/cpp/Loader.cpp}

\section{Anexa 14. PytorchModel.h}
\label{appendix:14_ptmodel_h}
\inputminted[linenos,tabsize=4,breaklines]{C++}{code/cpp/PytorchModel.h}

\section{Anexa 15. PytorchModel.cpp}
\label{appendix:15_ptmodel_cpp}
\inputminted[linenos,tabsize=4,breaklines]{C++}{code/cpp/PytorchModel.cpp}

\section{Anexa 16. raycasting.vert}
\label{appendix:16_raycasting_vert}
\inputminted[linenos,tabsize=4,breaklines]{C++}{code/cpp/raycasting.vert}

\section{Anexa 17. raycasting.frag}
\label{appendix:17_raycasting_frag}
\inputminted[linenos,tabsize=4,breaklines]{C++}{code/cpp/raycasting.frag}

% PYTHON

\section{Anexa 18. run.py}
\label{appendix:18_run_py}
\inputminted[linenos,tabsize=4,breaklines]{py}{code/python/run.py}

\section{Anexa 19. jobs.py}
\label{appendix:19_jobs_py}
\inputminted[linenos,tabsize=4,breaklines]{py}{code/python/jobs.py}

\section{Anexa 20. util.py}
\label{appendix:20_util_py}
\inputminted[linenos,tabsize=4,breaklines]{py}{code/python/util.py}


\section{Anexa 21. data/loading.py}
\label{appendix:21_data_load_py}
\inputminted[linenos,tabsize=4,breaklines]{py}{code/python/data/loading.py}

\section{Anexa 22. data/visualization.py}
\label{appendix:22_data_visualization_py}
\inputminted[linenos,tabsize=4,breaklines]{py}{code/python/data/visualization.py}

\section{Anexa 23. data/generic.py}
\label{appendix:23_data_generic_py}
\inputminted[linenos,tabsize=4,breaklines]{py}{code/python/data/generic.py}

\section{Anexa 24. data/ct\_org.py}
\label{appendix:24_data_ct_org_py}
\inputminted[linenos,tabsize=4,breaklines]{py}{code/python/data/ct_org.py}


\section{Anexa 25. model/train.py}
\label{appendix:25_model_train_py}
\inputminted[linenos,tabsize=4,breaklines]{py}{code/python/model/train.py}

\section{Anexa 26. model/test.py}
\label{appendix:26_model_test_py}
\inputminted[linenos,tabsize=4,breaklines]{py}{code/python/model/test.py}

\section{Anexa 27. model/loading.py}
\label{appendix:27_model_loading_py}
\inputminted[linenos,tabsize=4,breaklines]{py}{code/python/model/loading.py}

\section{Anexa 28. model/deploy.py}
\label{appendix:28_model_deploy_py}
\inputminted[linenos,tabsize=4,breaklines]{py}{code/python/model/deploy.py}

\section{Anexa 29. model/\_\_init\_\_.py}
\label{appendix:29_model___init___py}
\inputminted[linenos,tabsize=4,breaklines]{py}{code/python/model/__init__.py}

\section{Anexa 30. model/unet3d.py}
\label{appendix:30_model_unet3d_py}
\inputminted[linenos,tabsize=4,breaklines]{py}{code/python/model/unet3d.py}

% YAML

\section{Anexa 31. config/config.yaml}
\label{appendix:31_config_config_yaml}
\inputminted[linenos,tabsize=4,breaklines]{yaml}{code/python/config/config.yaml}

\section{Anexa 32. config/base\_data.yaml}
\label{appendix:32_config_base_data_yaml}
\inputminted[linenos,tabsize=4,breaklines]{yaml}{code/python/config/base_data.yaml}

\section{Anexa 33. config/ct\_org.yaml}
\label{appendix:33_config_ct_org_yaml}
\inputminted[linenos,tabsize=4,breaklines]{yaml}{code/python/config/ct_org.yaml}

\section{Anexa 34. config/base\_model.yaml}
\label{appendix:34_config_base_model_yaml}
\inputminted[linenos,tabsize=4,breaklines]{yaml}{code/python/config/base_model.yaml}

\section{Anexa 35. config/UNet3D.yaml}
\label{appendix:35_config_UNet3D_yaml}
\inputminted[linenos,tabsize=4,breaklines]{yaml}{code/python/config/UNet3D.yaml}

\section{Anexa 36. config/MyUNet3D.yaml}
\label{appendix:36_config_MyUNet3D_yaml}
\inputminted[linenos,tabsize=4,breaklines]{yaml}{code/python/config/MyUNet3D.yaml}

\section{Anexa 37. config/load\_data.yaml}
\label{appendix:37_config_load_data_yaml}
\inputminted[linenos,tabsize=4,breaklines]{yaml}{code/python/config/load_data.yaml}

\section{Anexa 38. config/load\_model.yaml}
\label{appendix:38_config_load_model_yaml}
\inputminted[linenos,tabsize=4,breaklines]{yaml}{code/python/config/load_model.yaml}

\section{Anexa 39. config/train\_model.yaml}
\label{appendix:39_config_train_model_yaml}
\inputminted[linenos,tabsize=4,breaklines]{yaml}{code/python/config/train_model.yaml}

\section{Anexa 40. config/test\_model.yaml}
\label{appendix:40_config_test_model_yaml}
\inputminted[linenos,tabsize=4,breaklines]{yaml}{code/python/config/test_model.yaml}

\section{Anexa 41. config/deploy.yaml}
\label{appendix:41_config_deploy_yaml}
\inputminted[linenos,tabsize=4,breaklines]{yaml}{code/python/config/deploy.yaml}
